\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-07-19 ms/ms.tex
biorxiv version
r1

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{authblk} % for title page
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{fancyhdr}
  \pagestyle{fancy}
  \renewcommand{\headrulewidth}{0pt} % remove line below header
  \lhead{\textit{Leaf energy budgets in R}} % running head
  \chead{}
  \rhead{}
\usepackage{footnote}
  \makesavenoteenv{tabular}
\usepackage{lineno}
  \linenumbers
\usepackage{lscape}
\usepackage{natbib}
\usepackage[parfill]{parskip}
\usepackage{setspace}
  \setstretch{1.5}
\usepackage{Sweave}
\input{ms-concordance}
  \DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em,frame=single}
  \DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em,frame=single}

@@

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Default parameter inputs  
>   leaf_par   <- make_leafpar()
>   enviro_par <- make_enviropar()
>   constants  <- make_constants()
>   # Solve for T_leaf
>   T_leaf <- tleaf(leaf_par, enviro_par, constants,
+                   quiet = TRUE)
> 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
>   library(tealeaves)
>   # Custom parameter inputs
>   leaf_par   <- make_leafpar(
+     replace = list(
+       leafsize = set_units(c(0.0025, 0.025, 0.25), "m")
+       )
+   )
>   enviro_par <- make_enviropar(
+     replace = list(
+       T_air = set_units(seq(275, 310, 5), "K")
+       )
+   )
>   constants  <- make_constants()
>   # Solve for T_leaf over a range of T_air
>   T_leaves <- tleaves(leaf_par, enviro_par, constants, 
+                       quiet = TRUE)
> 
\end{Sinput}
\end{Schunk}

@@

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=\textwidth,height=\textwidth]{../figures/fig1.pdf}}
\end{figure}

\begin{figure}[t!]
\caption{Extended examples of \tealeaves. Code to generate these examples is provided in the Supporting Information. A. The temperature of smaller leaves is more closely coupled to air temperature. Each line represents a different leaf size (small, dashed line; medium, dotted line; large, solid line) and the leaf-to-air temperature differential ($y$-axis) over an air temperature gradient ($x$-axis). B. Greater stomatal conductance cools leaves. Each line represents a different stomatal conductance (low, dashed line, 1 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; medium, dotted line, 3 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; high, solid line, 5 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$) and the leaf-to-air temperature differential ($y$-axis) over a gradient of incident solar radiation ($x$-axis). C. Forced convection dominates in small leaves; free convection dominates in very large leaves. Leaf size is indicated by line type as in Panel A. Vertical lines indicate approximate shifts from forced convection ($\mathit{Ar} < 0.1$), mixed convection ($0.1 < \mathit{Ar} < 10$), and free convection ($\mathit{Ar} > 10$). Small leaves always experience forced convection, leading to lower leaf temperature compared to large leaves experiencing free convection. D. Amphistomatous leaves (Stomatal Ratio $\sim$ 0.5) evaporate more than hypo- or hyperstomatous leaves (Stomatal Ratio $\sim$ 0 or 1, respectively), especially under free convection (low wind speed, $u$).}
\label{fig:fig1}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$                 & \code{leafsize}  & leaf characteristic dimension & m \\
  $\alpha_\mathrm{l}$ & \code{abs\_l}    & absorbtivity of longwave radiation (4 - 80 $\mu$m) & none \\
  $\alpha_\mathrm{s}$ & \code{abs\_s}    & absorbtivity of shortwave radiation (0.3 - 4 $\mu$m) & none \\
  $g_\mathrm{sw}$     & \code{g\_sw}     & stomatal conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $g_\mathrm{uw}$     & \code{g\_uw}     & cuticular conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $\mathit{sr}$       & \code{logit\_sr} & stomatal ratio (logit transformed) & none \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$              & \code{P}       & atmospheric pressure & kPa \\
  $r$              & \code{r}       & reflectance for short-wave irradiance (albedo) & none \\
  $\mathit{RH}$    & \code{RH}      & relative humidity    & none \\
  $S_\mathrm{sw}$  & \code{S\_sw}   & incident short-wave (solar) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{air}$ & \code{T\_air}  & air temperature      & K \\
  $u$              & \code{wind}    & windspeed            & m s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $a, b, c, d$     & \code{a, b, c, d} & coefficients for calculating $\mathit{Nu}$ and $\mathit{Sh}$ numbers & none \\
  $c_p$            & \code{c\_p}    & heat capacity of air & 1.01 J g$^{-1}$ K$^{-1}$ \\
  $D_{h,0}$        & \code{D\_h0}   & diffusion coefficient for heat in air at 0 °C & $19.0 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{m,0}$        & \code{D\_m0}   & diffusion coefficient for momentum in air at 0 °C & $13.3 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{w,0}$        & \code{D\_w0}   & diffusion coefficient for water vapour in air at 0 °C & $21.2 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $\epsilon$       & \code{epsilon} & ratio of water to air molar masses & 0.622 \\
  $\mathit{eT}$    & \code{eT}      & exponent for temperature dependence of diffusion & 1.75 \\
  $G$              & \code{G}       & gravitational acceleration & 9.8 m s$^{-2}$ \\
  $R$              & \code{R}       & ideal gas constant & 8.3144598 J mol$^{-1}$ K$^{-1}$ \\
  $R_\mathrm{air}$ & \code{R\_air}  & specific gas constant for dry air & 287.058 J kg$^{-1}$ K$^{-1}$ \\
  $\sigma$         & \code{s}       & Stephan-Boltzmann constant & $5.67 \times 10 ^ {-8}$ W m$^{-2}$ K$^{-4}$ \\

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $E$                 & \code{E}         & transpiration rate & mol m$^{-2}$ s$^{-1}$ \\
  $g_\mathrm{h}$      & \code{g\_h}      & boundary layer conductance to heat & m s$^{-1}$ \\
  $g_\mathrm{bw}$     & \code{g\_bw}     & boundary layer conductance to water vapour & m s$^{-1}$ \\
  $g_\mathrm{tw}$     & \code{g\_tw}     & total conductance to water vapour & m s$^{-1}$ \\
  $\mathit{Gr}$       & \code{Gr}        & Grashof number & none \\
  $H$                 & \code{H}         & sensible heat loss & W m$^{-2}$ \\
  $L$                 & \code{L}         & latend heat loss & W m$^{-2}$ \\
  $\mathit{Nu}$       & \code{Nu}        & Nusselt number & none \\
  $R_\mathrm{abs}$    & \code{R\_abs}    & absorbed radiation & W m$^{-2}$ \\
  $\mathit{Re}$       & \code{Re}        & Reynolds number & none \\
  $S_\mathrm{r}$      & \code{S\_r}      & infrared re-radiation & W m$^{-2}$ \\
  $\mathit{Sh}$       & \code{Sh}        & Sherwood number & none \\
  \tleaf              & \code{T\_leaf}   & leaf temperature & K \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $d_\mathrm{wv}$  & \code{d\_wv}   & water vapour pressure differential & mol m$^{-3}$ \\
  $h_\mathrm{vap}$ & \code{h\_vap}  & latent heat of vapourization & J mol$^{-1}$ \\
  $P_\mathrm{a}$   & \code{P\_a}    & density of dry air & g m$^{-3}$ \\
  $p_\mathrm{air}$ & \code{p\_air}  & water vapour pressure of the air & kPa \\
  $p_\mathrm{sat}$ & \code{p\_sat}  & saturating water vapour pressure & kPa \\
  $S_\mathrm{lw}$  & \code{S\_lw}   & incident long-wave (thermal infrared) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{sky}$ & \code{T\_sky}  & clear sky temperature & K \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $D_h$            & \code{D\_h}    & diffusion coefficient for heat in air at a given temperature & m$^2$ s$^{-1}$ \\
  $D_m$            & \code{D\_m}    & diffusion coefficient for momentum in air at a given temperature & m$^2$ s$^{-1}$ \\
  $D_w$            & \code{D\_w} & diffusion coefficient for water vapour in air at a given temperature        & m$^2$ s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Convergence diagnostics:}} \\
  \\
                   & \code{value} & energy balance at equilibrium \tleaf & W m$^{-2}$ \\
                   & \code{convergence} & 0 = converged; 1 = failed & none \\

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=\textheight]{../figures/pars.pdf}}
\end{figure}

@@

R code for running extended examples (Fig. \ref{fig:fig1}). The below code and the code to generate figures are deposited on GitHub (https://github.com/cdmuir/tealeaves-ms).

\begin{Schunk}
\begin{Sinput}
> # Extended example 1: 
> # leaf size and leaf-to-air temperature differential
> 
> library(tealeaves)
> lp  <- make_leafpar(
+   replace = list(
+     leafsize = set_units(c(0.005, 0.1, 0.4), "m")
+   )
+ )
> ep <- make_enviropar(
+   replace = list(
+     S_sw = set_units(660, "W/m^2"),
+     T_air = set_units(seq(278.15, 308.15, 5), "K")
+   )
+ )
> exe1 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
+                 set_units = TRUE, parallel = TRUE)
> 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> # Extended example 2: 
> # Solar radiation and leaf-to-air temperature differential
> 
> library(tealeaves)
> lp  <- make_leafpar(
+   replace = list(
+     g_sw = set_units(c(1, 3, 5), "umol/m^2/s/Pa")
+   )
+ )
> ep <- make_enviropar(
+   replace = list(
+     S_sw = set_units(seq(50, 950, 100), "W/m^2")
+   )
+ )
> exe2 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
+                 set_units = TRUE, parallel = TRUE)
> 
\end{Sinput}
\end{Schunk}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{authblk} % for title page
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{fancyhdr}
  \pagestyle{fancy}
  \renewcommand{\headrulewidth}{0pt} % remove line below header
  \lhead{\textit{Leaf energy budgets in R}} % running head
  \chead{}
  \rhead{}
\usepackage{footnote}
  \makesavenoteenv{tabular}
\usepackage{lineno}
  \linenumbers
\usepackage{lscape}
\usepackage{natbib}
\usepackage[parfill]{parskip}
\usepackage{setspace}
  \setstretch{1.5}
\usepackage{Sweave}
\input{ms-concordance}
  \DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em,frame=single}
  \DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em,frame=single}
\usepackage{xcolor}

@@

\begin{Schunk}
\begin{Sinput}
   library(tealeaves)
   # Default parameter inputs  
   leaf_par   <- make_leafpar()
   enviro_par <- make_enviropar()
   constants  <- make_constants()
   # Solve for T_leaf
   T_leaf <- tleaf(leaf_par, enviro_par, constants,
                   quiet = TRUE)

\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
   library(tealeaves)
   # Custom parameter inputs
   leaf_par   <- make_leafpar(
     replace = list(
       leafsize = set_units(c(0.0025, 0.025, 0.25), "m")
       )
   )
   enviro_par <- make_enviropar(
     replace = list(
       T_air = set_units(seq(275, 310, 5), "K")
       )
   )
   constants  <- make_constants()
   # Solve for T_leaf over a range of T_air
   T_leaves <- tleaves(leaf_par, enviro_par, constants, 
                       quiet = TRUE)

\end{Sinput}
\end{Schunk}

@@

%--------------------------------------------------
% Appendix
%--------------------------------------------------

\section*{Appendix: Theory}

This appendix describes how the components of leaf energy budgets (absorbed radiation, thermal infrared radiation loss, sensible heat flux, and latent heat flux) are modelled in \tealeaves. The model largely follows that previous developed by \citeauthor{Foster_Smith_1986} (\citeyear{Foster_Smith_1986}), so for brevity I have not explained every equation. I refer interested readers to \citeauthor{Nobel_2009} (\citeyear{Nobel_2009}), \citeauthor{Monteith_Unsworth_2013} (\citeyear{Monteith_Unsworth_2013}), and \citeauthor{Jones_2014} (\citeyear{Jones_2014}) for more background on the biophysics.

\subsection*{Absorbed radiation}

\begin{equation}
  R_\mathrm{abs} = \alpha_\mathrm{s} (1 + r) S_\mathrm{sw} + \alpha_\mathrm{l} \sigma (T_\mathrm{sky} ^ 4 + T_\mathrm{air} ^ 4).
\end{equation}

The left half of the equation calculates absorbed solar radiation. $\alpha_\mathrm{s}$ is the fraction of solar radiation absorbed. $S_\mathrm{sw}$ is the total incident radiation. This is multiplied by $1 + r$, where $r$ is the albedo of soil, to account for direct and reflected sunlight. The right half includes thermal infrared radiation. $\alpha_\mathrm{l}$ is the fraction of thermal infrared radiation absorbed. $\sigma$ is the Stefan-Boltzmann constant. As in \citeauthor{Okajima_etal_2012} (\citeyear{Okajima_etal_2012}), the clear sky temperature ($T_\mathrm{sky}$) is calculated as a function of air temperature ($T_\mathrm{air}$):

\begin{equation} \label{eq:Tsky}
  T_\mathrm{sky} = T_\mathrm{air} - \frac{20 S_\mathrm{sw}}{1000}.
\end{equation}

\citeauthor{Okajima_etal_2012} (\citeyear{Okajima_etal_2012}) define $T_\mathrm{sky}$ as the ``effective sky radiation temperature'' of ``cloudless sky''.

\subsection*{Thermal infrared radiation loss}

Both leaf surfaces lose thermal infrared radiation as a function of leaf emissivity (equal to the infrared absorption, $\alpha_\mathrm{l}$) and air temperature \citep{Foster_Smith_1986, Okajima_etal_2012}:

\begin{equation}
  S_\mathrm{r} = 2 \sigma \alpha_\mathrm{l} T_\mathrm{air} ^ 4.
\end{equation}

\subsection*{Sensible heat flux}

\begin{equation}
  H = P_\mathrm{a} c_p g_\mathrm{h} (T_\mathrm{leaf} - T_\mathrm{air}).
\end{equation}

$c_p$ is the heat capacity of air. The density of dry air ($P_\mathrm{a}$) is calculated as in \citeauthor{Foster_Smith_1986} (\citeyear{Foster_Smith_1986}):

\begin{equation}
  P_\mathrm{a} = \frac{2 P}{R_\mathrm{air} (T_\mathrm{leaf} - T_\mathrm{air})}.
\end{equation}

$P$ is the atmospheric pressure and $R_\mathrm{air}$ is the specific gas constant for dry air. \tealeaves~sums the boundary layer conductance to heat for both the upper and lower surface following \citeauthor{Foster_Smith_1986} (\citeyear{Foster_Smith_1986}), assuming a horizontal leaf orientation:

\begin{equation} \label{eq:g_h}
  g_\mathrm{h} = \frac{D_h \mathit{Nu}}{d}.
\end{equation}

$\mathit{Nu}$ is the unitless Nusselt number (defined below) and $d$ is the characteristic leaf dimension, a thermally relevant measure of leaf size. The diffusion coefficient of heat in air ($D_h$) is a function of temperature and pressure:

\begin{equation} \label{eq:D_x}
    D_\mathrm{h} = D_\mathrm{h,0} \Big(\frac{T}{273.15}\Big) ^ {\mathit{eT}} \frac{101.3246}{P}.
\end{equation}

\begin{align}
  \mathit{Nu}_\mathrm{forced} =  & ~ a \mathit{Re} ^ b \\
  \mathit{Nu}_\mathrm{free} =    & ~ c \mathit{Gr} ^ d.
\end{align}

$a, b, c, d$ are constants that depend on whether flow is laminar or turbulent and the direction of flow in the case of free convection (see below). In general, when the Archimedes number (also called the Richardson number) $\mathit{Ar} = \mathit{Gr} / \mathit{Re} ^ 2 \ll 0.1$, free convection dominates; when $\mathit{Ar} = \mathit{Gr} / \mathit{Re} ^ 2 \gg 10$, forced convection dominates \citep{Nobel_2009}. The Nusselt number coefficients can be found in \citeauthor{Monteith_Unsworth_2013} (\citeyear{Monteith_Unsworth_2013}). For forced convection, flow is laminar if $\mathit{Re} < 4000$, $a = 0.6, b = 0.5$; flow is turbulent if $\mathit{Re} > 4000$, $a = 0.032, b = 0.8$. These cutoffs for leaves are lower than for artificial surfaces because trichomes and other anatomical features of leaf surfaces induce turbulence more readily \citep{Grace_Wilson_1976}. For free convection, flow is laminar. For the upper surface when $T_\mathrm{leaf} > T_\mathrm{air}$ or the lower surface when $T_\mathrm{leaf} < T_\mathrm{air}$, $c = 0.5, d = 0.25$. Conversely, for the lower surface when $T_\mathrm{leaf} > T_\mathrm{air}$ or the upper surface when $T_\mathrm{leaf} < T_\mathrm{air}$, $c = 0.23, d = 0.25$.

Grashof and Reynolds numbers approximate the ratio of bouyant or inertial (numerator in equations below), respectively, to viscous forces (denominator in equations below). They are calculated as:

\begin{align} \label{eq:GrRe}
  \mathit{Gr} & = \frac{G d ^ 3 |T_{v,\mathrm{leaf}} - T_{v,\mathrm{air}}|}{T_\mathrm{air} D_m ^ 2} \\
  \mathit{Re} & = \frac{u d}{D_m}.
\end{align}

$G$ is the gravitational constant and $u$ is wind speed. The diffusion coefficient for momentum in air ($D_m$) is calculated for a given temperature following the same procedure above for heat diffusion ($D_h$; see Eq.~\ref{eq:D_x}). The virtual temperature is calculated according to \citeauthor{Monteith_Unsworth_2013} (\citeyear{Monteith_Unsworth_2013}) assuming that the leaf airspace is fully saturated while the air is has a vapour pressure decifit of $p_\mathrm{air}$:

\begin{align} \label{eq:Tv}
  T_{v, \mathrm{air}} & = T_\mathrm{air} / (1 - (1 - \epsilon) (p_\mathrm{air} / P)) \\
  T_{v, \mathrm{leaf}} & = T_\mathrm{leaf} / (1 - (1 - \epsilon) (p_\mathrm{sat} / P)).
\end{align}

$\epsilon$ is the ratio of water to air molar masses. The saturation water vapour pressure $p_\mathrm{sat}$ as a function of temperature is calculated using the Goff-Gratch equation \citep{Vomel_2016}. The vapour pressure of air is calculated from the relative humidity ($\mathit{RH}$) as $p_\mathrm{air} = \mathit{RH} p_\mathrm{sat}$.

\subsection*{Latent heat flux and evaporation}

Latent heat flux is the product of the latent heat of vaporization, the total leaf conductance to water vapour, and the water vapour gradient:

\begin{equation}
  L = h_\mathrm{vap} g_\mathrm{tw} d_\mathrm{wv}.
\end{equation}

\begin{equation}
  h_\mathrm{vap} = 56847.68250~[\mathrm{J~mol}^{-1}] - 43.12514~[\mathrm{J~mol}^{-1}~\mathrm{K}^{-1}]~T~[K].
\end{equation}

The water vapour pressure differential ($d_\mathrm{wv}$) from the inside to the outside of the leaf is the water vapor pressure inside the leaf, which is assumed to be saturated ($p_\mathrm{leaf} = p_\mathrm{sat}$), minus the water vapor pressure of the air ($p_\mathrm{air}$), calculated as described above. This value is converted from kPa to mol m$^{-3}$ using the ideal gas law:

\begin{equation}
  \label{eq:d_wv}
  d_\mathrm{wv} = p_\mathrm{leaf} / (\bar{R} T_\mathrm{leaf}) - RH p_\mathrm{air} / (\bar{R} T_\mathrm{air}).
\end{equation}

$\bar{R}$ is the ideal gas constant. The total conductance to water vapor ($g_\mathrm{tw}$) is the sum of the parallel lower (usually abaxial) and upper (usually adaxial) conductances

\begin{equation}
  \label{eq:g_tw}
  g_\mathrm{tw} = g_\mathrm{w,lower} + g_\mathrm{w,upper}.
\end{equation}

\begin{align}
  g_\mathrm{sw,lower} & = [g_\mathrm{sw} (1 - \mathit{sr})] [R (T_\mathrm{leaf} + T_\mathrm{air}) / 2] \\
  g_\mathrm{uw,lower} & = (g_\mathrm{uw} / 2) [R (T_\mathrm{leaf} + T_\mathrm{air}) / 2].
\end{align}

\begin{align}
  g_\mathrm{sw,upper} & = (g_\mathrm{sw} \mathit{sr}) [R (T_\mathrm{leaf} + T_\mathrm{air}) / 2] \\
  g_\mathrm{uw,upper} & = g_\mathrm{uw,lower}.
\end{align}

Partitioning total stomatal and cuticular conductance to water vapor across surfaces is not typically part of leaf energy budget models. However, stomatal \citep{Muir_2015} and cuticular \citep{Karbulkova_etal_2008} conductance can differ dramatically on each surface, so it could be useful modify these parameters, especially if leaf temperature models are integrated with photosynthetic models \citep{Muir_2019c}.

\begin{equation}
  g_\mathrm{bw} = \frac{D_w \mathit{Sh}}{d}.
\end{equation}

The diffusion coefficient for water vapor in air at a given temperature ($D_w$) is calculated using the Eq.~\ref{eq:D_x}, except that is $D_{w,0}$ is substituted for $D_{h,0}$. Each surface has its own Sherwood number ($\mathit{Sh}$):

\begin{align}
  \mathit{Sh}_\mathrm{forced} & = \mathit{Nu}_\mathrm{forced} (D_h / D_w) ^ \frac{1}{3} \\
  \mathit{Sh}_\mathrm{free} & = \mathit{Nu}_\mathrm{free} (D_h / D_w) ^ \frac{1}{4}.
\end{align}

\begin{equation}
  \label{eq:sherwood}
  \mathit{Sh} ^ {3.5} = \mathit{Sh}_\mathrm{forced} ^ {3.5} + \mathit{Sh}_\mathrm{free} ^ {3.5}.
\end{equation}

\begin{equation}
  E = g_\mathrm{tw} d_\mathrm{wv}.
\end{equation}

@@

\begin{figure}[ht]
\centerline{\includegraphics[height=\textheight,keepaspectratio]{../figures/fig1.pdf}}
\end{figure}

\begin{figure}[t!]
\caption{The leaf energy budget model in \tealeaves~takes environmental and leaf parameters to find the equilibrium leaf temperature ($T_\mathrm{leaf}$) at which incoming energy exactly matches outgoing energy. Under typical daytime conditions, this means thermal infrared radiation losses, sensible heat loss, and latent heat loss must balance absorbed radiation. A. The components of leaf energy budgets (thin orange lines) vary with leaf temperature (\textit{x}-axis). $T_\mathrm{leaf}$ is where the net energy flux (thick blue line) is 0 (blue point; see Eqn 1). B. 1) Radiation is emitted from sunlight and surrounding objects is absorbed by the leaf. 2) The leaf radiates some energy. 3) Heat is lost through convection when the leaf temperature is greater than air temperature. 4) Latent heat is lost through evaporation, which is driven by the vapor pressure deficit between the air and leaf interior and the leaf conductance to water vapor. Calculations used the following leaf parameter values in this example: $d = 0.1$ m; $\alpha_\mathrm{s} = 0.5$; $\alpha_\mathrm{l} = 0.97$; $g_\mathrm{sw} = 5~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $g_\mathrm{uw} = 0.1~\mu \textrm{mol}~\textrm{m} ^ {-2}~\textrm{s} ^ {-1}~\textrm{Pa} ^ {-1}$; $\mathit{SR} = 0.5$. Calculations used the following environmental parameter values in this example: $P = 101.3246$ kPa; $r = 0.2$; $\mathit{RH} = 0.5$; $S_\mathrm{sw} = 1000$ W m$^{-2}$; $T_\mathrm{air} = 298.15$ K; $u = 2$ m s$^{-1}$. See Table \ref{table:table_input} for symbol definitions.}
\label{fig:fig1}
\end{figure}

\begin{figure}[ht]
\centerline{\includegraphics[width=\textwidth,height=\textwidth]{../figures/fig2.pdf}}
\end{figure}

\begin{figure}[t!]
\caption{Extended examples of \tealeaves. Code to generate these examples is provided in the Supporting Information. A. The temperature of smaller leaves is more closely coupled to air temperature. Each line represents a different leaf size (small, dashed line; medium, dotted line; large, solid line) and the leaf-to-air temperature differential ($y$-axis) over an air temperature gradient ($x$-axis). B. Greater stomatal conductance cools leaves. Each line represents a different stomatal conductance (low, dashed line, 1 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; medium, dotted line, 3 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; high, solid line, 5 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$) and the leaf-to-air temperature differential ($y$-axis) over a gradient of incident solar radiation ($x$-axis). C. Forced convection dominates in small leaves; free convection dominates in very large leaves. Leaf size is indicated by line type as in Panel A. Vertical lines indicate approximate shifts from forced convection ($\mathit{Ar} < 0.1$), mixed convection ($0.1 < \mathit{Ar} < 10$), and free convection ($\mathit{Ar} > 10$). Small leaves always experience forced convection, leading to lower leaf temperature compared to large leaves experiencing free convection. D. Amphistomatous leaves (Stomatal Ratio $\sim$ 0.5) evaporate more than hypo- or hyperstomatous leaves (Stomatal Ratio $\sim$ 0 or 1, respectively), especially under free convection (low wind speed, $u$).}
\label{fig:fig2}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$                 & \code{leafsize}  & leaf characteristic dimension & m \\
  $\alpha_\mathrm{l}$ & \code{abs\_l}    & absorbtivity of longwave radiation (4 - 80 $\mu$m) & none \\
  $\alpha_\mathrm{s}$ & \code{abs\_s}    & absorbtivity of shortwave radiation (0.3 - 4 $\mu$m) & none \\
  $g_\mathrm{sw}$     & \code{g\_sw}     & stomatal conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $g_\mathrm{uw}$     & \code{g\_uw}     & cuticular conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $\mathit{sr}$       & \code{logit\_sr} & stomatal ratio (logit transformed) & none \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$              & \code{P}       & atmospheric pressure & kPa \\
  $r$              & \code{r}       & reflectance for short-wave irradiance (albedo) & none \\
  $\mathit{RH}$    & \code{RH}      & relative humidity    & none \\
  $S_\mathrm{sw}$  & \code{S\_sw}   & incident short-wave (solar) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{air}$ & \code{T\_air}  & air temperature      & K \\
  $u$              & \code{wind}    & wind speed            & m s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $a, b, c, d$     & \code{a, b, c, d} & coefficients for calculating $\mathit{Nu}$ and $\mathit{Sh}$ numbers & none \\
  $c_p$            & \code{c\_p}    & heat capacity of air & 1.01 J g$^{-1}$ K$^{-1}$ \\
  $D_{h,0}$        & \code{D\_h0}   & diffusion coefficient for heat in air at 0 °C & $19.0 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{m,0}$        & \code{D\_m0}   & diffusion coefficient for momentum in air at 0 °C & $13.3 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{w,0}$        & \code{D\_w0}   & diffusion coefficient for water vapour in air at 0 °C & $21.2 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $\epsilon$       & \code{epsilon} & ratio of water to air molar masses & 0.622 \\
  $\mathit{eT}$    & \code{eT}      & exponent for temperature dependence of diffusion & 1.75 \\
  $G$              & \code{G}       & gravitational acceleration & 9.8 m s$^{-2}$ \\
  $\bar{R}$        & \code{R}       & ideal gas constant & 8.3144598 J mol$^{-1}$ K$^{-1}$ \\
  $R_\mathrm{air}$ & \code{R\_air}  & specific gas constant for dry air & 287.058 J kg$^{-1}$ K$^{-1}$ \\
  $\sigma$         & \code{s}       & Stefan-Boltzmann constant & $5.67 \times 10 ^ {-8}$ W m$^{-2}$ K$^{-4}$ \\

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $E$                 & \code{E}         & transpiration rate & mol m$^{-2}$ s$^{-1}$ \\
  $g_\mathrm{h}$      & \code{g\_h}      & boundary layer conductance to heat & m s$^{-1}$ \\
  $g_\mathrm{bw}$     & \code{g\_bw}     & boundary layer conductance to water vapour & m s$^{-1}$ \\
  $g_\mathrm{tw}$     & \code{g\_tw}     & total conductance to water vapour & m s$^{-1}$ \\
  $\mathit{Gr}$       & \code{Gr}        & Grashof number & none \\
  $H$                 & \code{H}         & sensible heat flux & W m$^{-2}$ \\
  $L$                 & \code{L}         & latend heat flux & W m$^{-2}$ \\
  $\mathit{Nu}$       & \code{Nu}        & Nusselt number & none \\
  $R_\mathrm{abs}$    & \code{R\_abs}    & absorbed radiation & W m$^{-2}$ \\
  $\mathit{Re}$       & \code{Re}        & Reynolds number & none \\
  $S_\mathrm{r}$      & \code{S\_r}      & thermal infrared radiation losses & W m$^{-2}$ \\
  $\mathit{Sh}$       & \code{Sh}        & Sherwood number & none \\
  \tleaf              & \code{T\_leaf}   & leaf temperature & K \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $d_\mathrm{wv}$  & \code{d\_wv}   & water vapour pressure differential & mol m$^{-3}$ \\
  $h_\mathrm{vap}$ & \code{h\_vap}  & latent heat of vapourization & J mol$^{-1}$ \\
  $P_\mathrm{a}$   & \code{P\_a}    & density of dry air & g m$^{-3}$ \\
  $p_\mathrm{air}$ & \code{p\_air}  & water vapour pressure of the air & kPa \\
  $p_\mathrm{sat}$ & \code{p\_sat}  & saturating water vapour pressure & kPa \\
  $S_\mathrm{lw}$  & \code{S\_lw}   & incident long-wave (thermal infrared) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{sky}$ & \code{T\_sky}  & clear sky temperature & K \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $D_h$            & \code{D\_h}    & diffusion coefficient for heat in air at a given temperature & m$^2$ s$^{-1}$ \\
  $D_m$            & \code{D\_m}    & diffusion coefficient for momentum in air at a given temperature & m$^2$ s$^{-1}$ \\
  $D_w$            & \code{D\_w} & diffusion coefficient for water vapour in air at a given temperature        & m$^2$ s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Convergence diagnostics:}} \\
  \\
                   & \code{value} & energy balance at equilibrium \tleaf & W m$^{-2}$ \\
                   & \code{convergence} & 0 = converged; 1 = failed & none \\

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=\textheight]{../figures/figS1.pdf}}
\end{figure}

@@

R code for running extended examples (Fig. \ref{fig:fig2}). The below code and the code to generate figures are deposited on GitHub (https://github.com/cdmuir/tealeaves-ms).

\begin{Schunk}
\begin{Sinput}
 # Extended example 1: 
 # leaf size and leaf-to-air temperature differential

 library(tealeaves)
 lp  <- make_leafpar(
   replace = list(
     leafsize = set_units(c(0.005, 0.1, 0.4), "m")
   )
 )
 ep <- make_enviropar(
   replace = list(
     S_sw = set_units(660, "W/m^2"),
     T_air = set_units(seq(278.15, 308.15, 5), "K")
   )
 )
 exe1 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
                 set_units = TRUE, parallel = TRUE)

\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
 # Extended example 2: 
 # Solar radiation and leaf-to-air temperature differential

 library(tealeaves)
 lp  <- make_leafpar(
   replace = list(
     g_sw = set_units(c(1, 3, 5), "umol/m^2/s/Pa")
   )
 )
 ep <- make_enviropar(
   replace = list(
     S_sw = set_units(seq(50, 950, 100), "W/m^2")
   )
 )
 exe2 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
                 set_units = TRUE, parallel = TRUE)

\end{Sinput}
\end{Schunk}
